---
title: "Lets Learn Everything Again"
author: "Karen Vieira"
date: "4/2/2020"
output: html_document
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Class Meeting 1 Review

##Functions

```{r}
vector_name_second <- c(4,5,6)
```

You create a vector like shown above name <- c()

```{r}
range(vector_name_second)
```
Functions always go on the left. For a list of functions go here: http://adv-r.had.co.nz/Vocabulary.html

```{r}
?mean
```

This is the help function. The help function allows you to figure out how a function works.

A fuction has arguments. 4 to be exact.

if an argument says something like name = value, this will have a defult and you do not need to give it any specific info about it, if an argument says X then you DO have to have something input there

```{r}
names(mtcars)
```

mtcars is an example of a data frame. There are also some functions here to better understand the data frame shown.

head() shows the first couple rows
tail() shows the last couple rows
nrow() tells you the number of rows you have
ncol() tells you the number of collums you have
summary() gives you quartile data for each variable
names() tells you what each variable is labeled as

```{r}
library(tibble)
browseVignettes(package = "tibble")
```

here are some helpful links when it comes to writing notes in markdown https://guides.github.com/pdfs/markdown-cheatsheet-online.pdf and https://rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf

```{r}

```

You can add a code chunk instantly by hitting command + alt + i

```{r}
library(gapminder)
library(tibble)
library(knitr)
library(DT)

as_tibble(mtcars) -> mtcars_tbl
```
make sure that the arrow is facing the name of the new vector you would like to create

##dataset printing

```{r}
print(mtcars_tbl)
```

```{r}
kable(mtcars_tbl)
```
print and kable look aesthetically different

```{r}
kable(gapminder)
```
you can only see first couple with kable on consel so to make it easier to look at use datatable() 
```{r}
datatable(gapminder)
```
Here you can use a search function and sort the data however you want

##YAML
The YAML header is something specific to RMarkdown. It can be used to change certain aspects of the file or how the output of the file is created. 
For types of things you can add and how to add them follow this link: https://bookdown.org/yihui/rmarkdown/html-document.html

###Class Meeting 2 Review

**If you are stuck at any point in an assignment this is a great resource for what to do: https://wiernik-datasci.netlify.com/help-general/**

It's important when asking questions to provide links to what you are having issues with. If you can't get an output these are the instructions for creating a reproducible example https://stackoverflow.com/help/minimal-reproducible-example

This is the link to use when you need to ask the class and Dr. Wiernik a question https://github.com/USF-Psych-DataSci-2020/Discussion/issues

###Class Meeting 3 Review


